---
title: "MARSS_Models_Script"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# data wrangling
library(xtable)
library(tidyverse)
library(broom)
library(forcats)

# time series packages
library(MARSS)

```

# Import derived data

From Dryad repository
See README files for more detailed metadata
```{r echo = T, results = "hide", messages = F}
# Water temperature - response variable
# Matrix of pond, creek, and Klamath River temperatures summarized as daily mean temperature 
# Includes data from 1 July 2020 to 13 July 2021 
daily_means_condensed <- readRDS('daily_means_condensed.rds')

# Air temperature - covariate data
# Matrix of air temperatures summarized as daily mean temperature
# Includes data from 1 July 2020 to 13 July 2021 
covariate <- readRDS('covariate.rds')
```

#Transform matrices
```{r}
z_daily_means_condensed <- zscore(daily_means_condensed)
z_covariate <- zscore(covariate)
```

# Hypothesis 1: all states have different levels of stochastic (Q) and deterministic (C) variability 
```{r}
# convention: name modhypothesis
mod1 = list()
mod1$A = "zero" 
mod1$Z = "identity"
mod1$R = "zero" 
mod1$Q = "diagonal and unequal" 
mod1$B = "diagonal and unequal" 
mod1$U = "zero"  
mod1$C = "unequal" 
mod1$c = z_covariate
mod1.fit = MARSS(z_daily_means_condensed, model=mod1)
mod1_params =MARSSparamCIs(mod1.fit)
MARSSparamCIs(mod1.fit)
saveRDS(mod1_params,"mod1_params.RDS")
```

```{r}
# plot residuals
par(mfrow=c(5,2), mai=c(0.1,0.5,0.2,0.1), omi=c(0.5,0,0,0))
  for (j in 1:5) {
    plot.ts(residuals<-MARSSresiduals(mod1.fit, type = "tt1")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
  }
```

#Test covariate lags
##Pull in slightly lagged air temp dataset
```{r}
airtemp_lag <- read.csv("SlaterButteAirTemp_2020_2021_lag.csv")

#Convert Fahrenheit to Celsius
airtemp_lag$TAVG <- fahrenheit.to.celsius(airtemp_lag$TAVG)
airtemp_lag$TMAX <- fahrenheit.to.celsius(airtemp_lag$TMAX)
airtemp_lag$TMIN <- fahrenheit.to.celsius(airtemp_lag$TMIN)

#Convert dates to appropriate format
airtemp_lag$date <- lubridate::mdy(airtemp_lag$DATE)
missing_data <- airtemp_lag[!complete.cases(airtemp_lag),] #No missing data
missing_data
airtemp_lag$day <- lubridate::floor_date(airtemp_lag$date, unit="day")
covariate_lag <- (t(airtemp_lag$TAVG))

#z score to fit with our data
z_covariate_lag <- zscore(covariate_lag)
```

```{r}
#t-0 no lag (1 July 2020 - 13 July 2021)
#Use original z_covariate matrix
str(z_covariate)
#t-1 lag (30 June 2020 - 12 July 2021)
z_covariate_t1 <- z_covariate_lag[c(16:393)]
z_covariate_t1 <- as.matrix(t(z_covariate_t1))
str(z_covariate_t1)

#t-2 lag (29 June 2020 - 11 July 2021)
z_covariate_t2 <- z_covariate_lag[c(15:392)]
z_covariate_t2 <- as.matrix(t(z_covariate_t2))
str(z_covariate_t2)

#t-3 lag (28 June 2020 - 10 July 2021)
z_covariate_t3 <- z_covariate_lag[c(14:391)]
z_covariate_t3 <- as.matrix(t(z_covariate_t3))
str(z_covariate_t3)
```


```{r}
#test best model(mod1) with lags
#t-1 lag
mod1a = mod1
mod1a$c = z_covariate_t1
mod1a.fit = MARSS(z_daily_means_condensed, model=mod1a)
mod1a_params =MARSSparamCIs(mod1a.fit)
MARSSparamCIs(mod1a.fit)
saveRDS(mod1a_params,"mod1a_params.RDS")
#AICc -9832.204 (better than mod1)

#t-2 lag
mod1b = mod1
mod1b$c = z_covariate_t2
mod1b.fit = MARSS(z_daily_means_condensed, model=mod1b)
mod1b_params =MARSSparamCIs(mod1b.fit)
MARSSparamCIs(mod1b.fit)
saveRDS(mod1b_params,"mod1b_params.RDS")
#AICc -9526.632 (worse than mod1)

#t-3 lag
mod1c = mod1
mod1c$c = z_covariate_t3
mod1c.fit = MARSS(z_daily_means_condensed, model=mod1c)
mod1c_params =MARSSparamCIs(mod1c.fit)
MARSSparamCIs(mod1c.fit)
saveRDS(mod1c_params,"mod1c_params.RDS")
#AICc -9418.625  (worse than mod1)

#Final decision: use t-1 covariate lag (dataset z_covariate_t1)
#All subsequent models use t-1 lag in covarite dataset
```

# Hypothesis 1 (with lag): all states have different levels of stochastic (Q) and deterministic (C) variability 
```{r}
# convention: name modhypothesis
mod1 = list()
mod1$A = "zero" 
mod1$Z = "identity"
mod1$R = "zero" 
mod1$Q = "diagonal and unequal" 
mod1$B = "diagonal and unequal" 
mod1$U = "zero"  
mod1$C = "unequal" 
mod1$c = z_covariate_t1
mod1.fit = MARSS(z_daily_means_condensed, model=mod1)
mod1_params =MARSSparamCIs(mod1.fit)
MARSSparamCIs(mod1.fit)
saveRDS(mod1_params,"mod1_params.RDS")
```
# Hypothesis 2: all states have save levels of stochastic (Q) and deterministic (C) variability
```{r}
# convention: name modhypothesis
mod2 = list()
mod2$A = "zero" 
mod2$Z = "identity"
mod2$R = "zero" 
mod2$Q = "diagonal and equal" 
mod2$B = "diagonal and equal" 
mod2$U = "zero"  
mod2$C = "equal" 
mod2$c = z_covariate_t1
mod2.fit = MARSS(z_daily_means_condensed, model=mod2)
mod2.params =MARSSparamCIs(mod2.fit)
MARSSparamCIs(mod2.fit)
```
```{r}
# plot residuals
par(mfrow=c(5,2), mai=c(0.1,0.5,0.2,0.1), omi=c(0.5,0,0,0))
  for (j in 1:5) {
    plot.ts(residuals<-MARSSresiduals(mod2.fit, type = "tt1")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
  }
```

# Hypothesis 3: Habitat type (Creeks vs ponds vs Klamath)
```{r}
# convention: name modhypothesis
mod3 = list()
## Modify matrices
# 1st: group time series into categories
hypothesis = c("pond","pond","pond","pond",
               "pond","pond","pond","pond",
               "pond","creek","creek","Klamath")

# 2nd: build C matrix (12 x 1)
mod3$C = matrix(hypothesis)
mod3$c = z_daily_means_condensed

# 3rd: build Q matrix (12 x 12, with "C vector" in its diagonal)
Q <-  matrix(list("pond",0,0,0,0,0,0,0,0,0,0,0,
                  0,"pond",0,0,0,0,0,0,0,0,0,0,
                  0,0,"pond",0,0,0,0,0,0,0,0,0,
                  0,0,0,"pond",0,0,0,0,0,0,0,0,
                  0,0,0,0,"pond",0,0,0,0,0,0,0,
                  0,0,0,0,0,"pond",0,0,0,0,0,0,
                  0,0,0,0,0,0,"pond",0,0,0,0,0,
                  0,0,0,0,0,0,0,"pond",0,0,0,0,
                  0,0,0,0,0,0,0,0,"pond",0,0,0,
                  0,0,0,0,0,0,0,0,0,"creek",0,0,
                  0,0,0,0,0,0,0,0,0,0,"creek",0,
                  0,0,0,0,0,0,0,0,0,0,0,"Klamath"),12,12)

# 4th: B, identical to Q
B <- Q

mod3$A = "zero" 
mod3$Z = "identity"
mod3$R = "zero" 
mod3$Q = Q 
mod3$B = Q
mod3$U = "zero"  
mod3$C = matrix(hypothesis) 
mod3$c = z_covariate_t1
mod3.fit = MARSS(z_daily_means_condensed, model=mod3)
mod3.params =MARSSparamCIs(mod3.fit)
MARSSparamCIs(mod3.fit)

```
```{r}
# plot residuals
par(mfrow=c(5,2), mai=c(0.1,0.5,0.2,0.1), omi=c(0.5,0,0,0))
  for (j in 1:5) {
    plot.ts(residuals<-MARSSresiduals(mod3.fit, type = "tt1")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
  }
```
# Hypothesis 4: Watershed (Horse Creek vs. Seiad Creek)
```{r}
# convention: name modhypothesis
mod4 = list()
## Modify matrices
# 1st: group time series into categories
rownames(z_daily_means_condensed)
hypothesis2 = c("SC","SC","SC","SC",
               "SC","HC","HC","HC",
               "HC","SC","HC","Klamath")

# 2nd: build C matrix (12 x 1)
mod4$C = matrix(hypothesis2)
mod4$c = z_daily_means_condensed

# 3rd: build Q matrix (12 x 12, with "C vector" in its diagonal)
Q <-  matrix(list("SC",0,0,0,0,0,0,0,0,0,0,0,
                  0,"SC",0,0,0,0,0,0,0,0,0,0,
                  0,0,"SC",0,0,0,0,0,0,0,0,0,
                  0,0,0,"SC",0,0,0,0,0,0,0,0,
                  0,0,0,0,"SC",0,0,0,0,0,0,0,
                  0,0,0,0,0,"HC",0,0,0,0,0,0,
                  0,0,0,0,0,0,"HC",0,0,0,0,0,
                  0,0,0,0,0,0,0,"HC",0,0,0,0,
                  0,0,0,0,0,0,0,0,"HC",0,0,0,
                  0,0,0,0,0,0,0,0,0,"SC",0,0,
                  0,0,0,0,0,0,0,0,0,0,"HC",0,
                  0,0,0,0,0,0,0,0,0,0,0,"Klamath"),12,12)

# 4th: B, identical as Q
B <- Q

mod4$A = "zero" 
mod4$Z = "identity"
mod4$R = "zero" 
mod4$Q = Q 
mod4$B = Q
mod4$U = "zero"  
mod4$C = matrix(hypothesis2) 
mod4$c = z_covariate_t1
mod4.fit = MARSS(z_daily_means_condensed, model=mod4)
mod4.params =MARSSparamCIs(mod4.fit)
MARSSparamCIs(mod4.fit)

```
```{r}
# plot residuals
par(mfrow=c(5,2), mai=c(0.1,0.5,0.2,0.1), omi=c(0.5,0,0,0))
  for (j in 1:5) {
    plot.ts(residuals<-MARSSresiduals(mod4.fit, type = "tt1")$model.residuals[j, ],
            ylab = "Residual")
    abline(h = 0, lty = "dashed")
    acf(residuals,na.action = na.pass)
  }
```

#AICc 
```{r}
data.frame(Model=c("mod1", "mod2", "mod3", "mod4"),
           AICc=round(c(mod1.fit$AICc,
                        mod2.fit$AICc,
                        mod3.fit$AICc,
                        mod4.fit$AICc),1))
```

#Plot Covariate Effects
```{r}
mod1_params <- readRDS("mod1_params.RDS")
mod1_df <- broom::tidy(mod1_params)
mod1_df_clip <- mod1_df[c(37:48),]
mod1_df_clip$name <- c("Alexander","Stender","Durazo","LowerSeiad","May","FishGulch","Goodman","UpperLaw","LowerLaw","SeiadCreek","HorseCreek","KlamathRiver")

mod1_df_clip$name <- factor(mod1_df_clip$name, levels = c("Alexander","Stender","Durazo","LowerSeiad","May","SeiadCreek","FishGulch","Goodman","UpperLaw","LowerLaw","HorseCreek","KlamathRiver"))

png("Fig_AirTempEffects.png", width = 500, height = 300)
ggplot()+
  geom_pointrange(data = mod1_df_clip, aes(x = name, y = estimate, ymin = conf.low, ymax = conf.up), color = "black") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Sites",
       y = "Air Temperature Effects") +
  ggtitle("Air Temperature Effects") +
  theme_classic()+
  theme(text=element_text(size=16),axis.text.x=element_text(angle = 45, hjust = 1))
dev.off()
```

